Visualization of [fulle name] Fractional Integrals

### 2019-04-11 fractional/CMJ style files/article-template.tex
added more text to example section

We can assign a geometric interpretation to the above fractional integrals by converting them into Cavalieri integrals. This can be achieved by first 
converting the above integrals into Riemann-Stieltjes integrals and then converting the resulting integrals into Cavalieri integrals. Exaclty how these conversion are 
to be performed is discussed in the previous section. The inegrator $g_t^{\alpha}(\tau)$ of the aforementioned intermediate Riemann-Stieltjes integrals are equal and independent of the integrand $f(\tau)$.
The set of functions $\{g_{10}^{\alpha}(\tau)|\alpha\in\{0,0.2,\cdots,0.8,1\}\}$ are presented in Table \textbf{??}. The integration limits of the aformentioned Cavalieri 
integrals are functions and are determined by the integrand $f(\tau)$ and the integrator $g_t^{\alpha}(\tau)$. The shape of the infini

>>>>

We can assign a geometric interpretation to the above fractional integrals by converting them into Cavalieri integrals. This can be achieved by first 
converting the above integrals into Riemann-Stieltjes integrals and then converting the resulting integrals into Cavalieri integrals. Exaclty how these conversion are 
to be performed is discussed in the previous section. The inegrator $g_t^{\alpha}(\tau)$ of the aforementioned intermediate Riemann-Stieltjes integrals are equal and independent of the integrand $f(\tau)$.
The set of functions $\{g_{10}^{\alpha}(\tau)|\alpha\in\{0,0.2,\cdots,0.8,1\}\}$ are presented in Table \textbf{??}. The integration limits of the aformentioned Cavalieri 
integrals are functions and are determined by the integrand $f(\tau)$ and the integrator $g_t^{\alpha}(\tau)$. Recall that a Cavalieri integral can 
be interpreted as an infinite sum of non-rectanguar infinitesimals whose shape is determined by its lower integration limit $a_t^{\alpha}(y)$. The list of functions 
$\{a_{10}^{\alpha}(y)|\alpha\in\{0,0.2,\cdots,0.8,1\}\}$ that can be associated with the integrals in Eq~{??} and Eq~{??} are presented in Table~\textbf{??}. Note that 
$a_t^{\alpha}(y)$ is not a static function it depends on the order of integration $\alpha$ and the integration limit $t$. The fact that $a_t^{\alpha}(y)$ is dependend 
on $t$ implies that a fractional integral of a particular order cannot be converted to a single Cavalieri integral, but rather to an infinite set $\mathcal{C}$ of Cavalieri integrals.
Each element of $\mathcal{C}$ can be associated with a particular choice of $t$.

\begin{figure}[htb]
\centering
\includegraphics[width=1\textwidth]{geo_int1.pdf}
\caption{A plot of $\Gamma(x)$. $\Gamma(x)$ is not defined for the non-negative integers.}
\label{fig:geo1}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=1\textwidth]{geo_int2.pdf}
\caption{A plot of $\Gamma(x)$. $\Gamma(x)$ is not defined for the non-negative integers.}
\label{fig:geo2}
\end{figure}
